Paper Analysis

### 2024-07-22 Paper_WriteUp/Paper_Plots.qmd
tidy up the data format, delete old incorrect results and update paths to reflect this

This will provide the final figures used in the paper.

@@

res_data_path <- rep(NA, 4)
res_data_path[1] <- here("results/lichess1700-1900_mar/")
res_data_path[2] <- here("results/lichess2000-2200_mar/")
res_data_path[3] <- here("results/lichess2300-2500_mar/")
res_data_path[4] <- here("results/lichessGrandmasters_mar/")

@@

data_path <- here("results/lichess1700-1900_mar")

@@

data_path <- here("results/lichess2000-2200_mar")

@@

data_path <- here("results/lichess2300-2500_mar")

@@

```{r}
data_path <- here("results/lichessGrandmasters_mar")

@@

data_path <- here("results/lichessGrandmasters_mar")

@@

perm_data_path <- here("results/lichess1700-1900_mar/perm")

@@

![Time-Varying PPC for 2000-2200](../results/lichess2000-2200_mar/time/ppc_fit_first_last_bullet.png)

![Time-Varying PPC for 2300-2500](../results/lichess2300-2500_mar/time/ppc_fit_first_last_bullet.png)

@@

```{r}
perm_data_path <- here("results/lichessGrandmasters_mar/perm/")

>>>>

This document will recreate all numeric and graphical
summaries contained in the submitted manuscript and the 
supplementary materials.

@@

res_data_path <- rep(NA, 4)
res_data_path[1] <- here("results/lichess1700-1900/")
res_data_path[2] <- here("results/lichess2000-2200/")
res_data_path[3] <- here("results/lichess2300-2500/")
res_data_path[4] <- here("results/lichessGrandmasters/")

@@

data_path <- here("results/lichess1700-1900")

@@

data_path <- here("results/lichess2000-2200")

@@

data_path <- here("results/lichess2300-2500")

@@

```{r}
data_path <- here("results/lichessGrandmasters")

@@

data_path <- here("results/lichessGrandmasters")

@@

perm_data_path <- here("results/lichess1700-1900/perm")

@@

![Time-Varying PPC for 2000-2200](../results/lichess2000-2200/time/ppc_fit_first_last_bullet.png)

![Time-Varying PPC for 2300-2500](../results/lichess2300-2500/time/ppc_fit_first_last_bullet.png)

@@

```{r}
perm_data_path <- here("results/lichessGrandmasters/perm/")
